\setlength{\parindent}{4em}
\setlength{\parskip}{0.5em}
\renewcommand{\baselinestretch}{1.0}

\subsubsection{Arrival at Kraghammer}

\hfill %Fills first line, causes proper indention; DO NOT REMOVE

\huge \textsc{K}\normalsize raghammer's door guards had only begrudgingly let the mixed group of individuals through to the dwarven citadel along with several pointers and biting remarks, but only after showing their recently gifted paperwork and documents. It seemed a third time was a charm they wouldn't need, and neither would they need any illegal entry tactics. They made their way down the dark tunnels and alleyways towards the central portion of the city proper, witnessing an enormous underground metropolis sprawl out before them from their heightened vantage within the vacuous cave. Around them, the dark earth and shadows were crafted into beautiful stone work, marble columns, archways, and labyrinthine bridges climbing across the vertical cityscape. All of which was warmed with the glow of some strange crimson rock peppered throughout the town as a light source. A large metal forge enveloped the center of this three-tiered cylindrical city that had been built directly into the mountain itself.

A Tal'Dorei Council arcanist, Allura Vysoren, had helped the group gain the necessary papers to enter Kraghammer on the request that they locate and return to the safety of Tal'Dorei a questing Halfling Paladin of Bahamut, the platinum dragon. The paladin, a well-known and respected Lady Kima of Vord, was a long-time friend of the human woman Allura, and had essentially left on a vision quest as part of her development as a paladin. However, when speaking to the friends about her request Allura let the information go that a dark vision had come to her, saying that some sort of evil root was beginning to brood beneath Kraghammer and the mountains within. 

No matter the case of why they were headed back to Kraghammer, the majority of the group was happy to have simply made it out of an ambush of roaming barbarian goliaths while on the road to the dwarven citadel, even if it was by a major stroke of luck. In the middle of fighting the fellow goliaths who ambushed them, Grog someohow recognized one of them as a former ally of his own and ---for the first and only time anyone in the group could remember--- managed to talk his way out of a fight, but of course not until after both parties had traded scrapes and blows.

What they knew of Lady Kima's last actions and whereabouts was that she was headed into a mithral mine where the evil was supposedly brewing. They learned along the way that most of the mithral market within Kraghammer, along with an equal majority of the mithral mines themselves, were owned by the dwarven Lord Nostoc Greyspine; this being the only name they had with any definite ties to the deep earth quarry, they paused in the middle of the pathway overlooking the cavernous center of Kraghammer's cylindrical shape and began to argue over what to do. 

Scanlan spoke up first and inquisitively to his companions who all, including his fellow gnome, Pike, towered above him. ``We have to go find him, don't we?" Percival was the first to respond, opening his palms while looking back and forth between his companions behind his peculiarly shaped glasses.
    
``I think, before we do anything, we should find a place to sleep."

``That's true!" Tiberius gruffly bellowed and quickly agreed, turning his bespectacled and fiery-red scaled head to face Percival.

Percival turned his head to face Tiberius as well, returning the agreement. ``Wouldn't it be nice to put everything down for a little while?" 

``Of course," Scanlan interjected while placing his hands on his hips and grinning. ``I have a lot of, uh ... \textit{booty} that I need to stow," at which several of his companions rolled their eyes and groaned at the carved and patterned ceiling of Kraghammer.

``I don't want to  ... hear about ... ughh..." Percival tilted back his head holding the bridge of his nose and sighed.

``Ha! Good way to phrase that, Scanlan." Tiberius complimented. ``Also," he added, returning his attention to the whole party, ``I would like to check out any kind of places where they might have enchanted libraries or whatnot." His dragonborn eyes slightly brightened with a small amount of excitement at the possibilities.

``Can---," Scanlan turned directly to Tiberius this time, ``Can you stay with us? You're the only one speaks Dwarvish."

``Yes, you are getting ahead of yourself." Vax'ildan commented, arms crossed.

``I'm just saying put it on the list!" Tiberius retorted with a hint of either annoyance or anger as he shrugged with his hands out.

Vax'ildan took a look around the area as he finished his part in the conversation and noticed two guards standing a small distance apart that were posted nearby wearing dark crimson and brass chest plates with a uniform scar carved across front that was actually a part of the design. The two guards were staring awkwardly at the colorful group arguing in the middle of one of Kraghammer's entry thoroughfares. Raising his hand in a slow swiping motion from Tiberius towards the two guards, Vax'ildan continued to stare back at the armored pair as he flatly spoke. 

``Tiberius, make with the dwarf-talk, please."

``Oh, uh---" Tiberius quickly stepped over to the dwarven pair, leaned down slightly and continued; ``Hello, friends." He  paused looking back and forth between the gaurds for just a moment before clearing his throat.``Ah-hrm... My associates and I were looking for a place of lodging for the night and a place of reputable ... reputation."

``You hear that, Jepson?" the dwarf closest to Tiberius shouted with a grin to the other. ``They're lookin' for a place to stay."

``Aye," the dwarf named Jepson shouted back. ``I heard that right. It's about time we had some \textit{new} folk in town." Jepson then looked to Tiberius who stood closer to his companion than himself. ``Well..." he said before turning and loudly answering in common-speak to the whole party, ``...if you're lookin' for a place to stay, I'd say your best bets would be the Pig Pits."

``Is that the \textit{name} of a place?" Scanlan asked worriedly as he slightly retracted at the name of such an establishment. 

``Yes!" replied Jepson with a self-satisfied grin that was kept well-hidden behind his beard. ``Certainly! The Pig Pits."

``Alright ..." Scanlan smiled worriedly, as Jepson continued; ``Ask for the Pig Pits---" before being cut off by Vex'ahlia.

``Those are \textit{actually} pig pits, aren't they?" she questioned while calmly stroking Trinket's fur with one of her hands. She looked immediately fed up with the dwarves for a moment as she asked, sure of the answer.

``I know, I feel like ... I feel like we're being hazed ... " Keyleth added shyly.

``What?! No!" Jepson drew out the length of the word `no' as if holding it would make it more convincing. ``Not at all." 

``That sounds alright with me." Grog said to none in particular, but Vex'ahlia turned, looked up towards him, and gave him a disapproving look which he returned with a fully contented smile.

Finally, Scanlan got over his trepidation of the supposed name of a potential inn, and kindly asked; ``Which way to the Pig Pits, sir?"

``Pig Pits," the dwarf closer to Tiberius turned slightly, and pointed a hand over the ledge of the thoroughfare, ``are that way." He pointed to an area down past the central forge structure in the city to the very bottom nearby a large temple the enveloped the bottom floor of Kraghammer proper. There was indeed a very distant slop of mud where internal livestock were being kept for the city. A place to sleep, certainly, but not a welcome one.

At this, Vex'ahlia pulled a piece of gold from her pockets and held it pointed up between two fingers and her thumb with her eyes closed for a moment. ``Please, sir, we're looking for a place to stay that isn't covered in mud."

Still pointing down to the Pig Pits, the dwarf looked over his shoulder. ``Oooh ... " he said as he turned and happily grinned ear to ear, impressed with the half-elf woman before him. ``Well, it's good to see that at least one of you speaks dwarvish." Sauntering over to her, the dwarf took the coin, kinked it in his teeth, and sighed with a happily defeated tone as he pocketed the coin. ``All right," he began, ``if you're looking for a proper place to stay you're going to look for the Iron Hearth Tavern. That is just to your left, up about that way," he pointed upwards to his right, up an incline in the ground of this tier of the city, ``no more than half a mile. Keep an eye out. Listen for the laughter---" he shook his fingers around his ears in a pantomime of the noise as he said this, ``and the people who are \textit{very}, very drunk. That's your best bet"

``Thanks." Vax'ahlia responded.

``No worries." the said dwarf. He began to speak again, but she quickly added;

``I like your armor, by the way." after which she winked, accentuating herself as she did so, but it was lost on the dwarf.

``Well, thank you kindly." He replied, turning around and making the short walk back to his post as Tiberius walked past him to rejoin the group.

They continued to the western side of Kraghammer, up in the direction the dwarves had guided them. Curling around the central platform of the city, the group made way to a large and central tavern-inn that could be clearly seen from well down the road. Just as the dwarf had told them to listen for, music was being played, laughter and boastful cheer was flooding the streets that centered around this tavern, and several arguments could be heard from the distance of the several-buildings between them and their hopeful place of rest. It was apparent from the multide of people entering and exiting the flourishing tavern-inn the dwarves had told them of was a significant part of the social life here on this level of the city.

Scanlan's nose crinkled as he walked first into the bustling tavern. He took a sniff of the air before turning in the doorway and announcing to the group, ``Something \textit{smells} in here."

``Drinking territory," Grog said in an unusually matter-of-fact tone, still outside the tavern--- his height kept his eyes just higher than the doorway, so as they grew closer he was unable to see for himself how the inside of the tavern was, nor did he receive the smells as strongly as his compatriots. 

Inside, loud, boisterous and hearty dwarven laughter was accompanied by clinking drinks, and the scent that Scanlan had sampled began to reach the other party members of the group; the place smelled of stale alcohol and smoked wood of some kind. Grog placed a large gray hand on the upper beam of the door frame and leaned downward to enter and was immediately hit by the scent and scenes. 

``Yes!" Grog suddenly exclaimed in his gruff voice, as a large smile quickly spread across his face and his eye lit up with excitement.

Most of the tables they could see looked to be in good condition, save a few which looked to be half-broken and repaired from what must have been some previous encounter within the bar. In the center of the room was what looked to be, although currently not in use, a specifically built brawling circle. It looked as though it had become more oval over time, however, as now from their distance it seemed to roughly measure 30 feet long by 20 feet wide. As the more average-height compatriots walked over to the brawling ring, its form cleared and they could tell it was, essentially, an octagon in shape. Grog ducked in after them to discover that what was a vaulted ceiling for the dwarves was only about the width of one of his fingers from the top of his head. Seven or eight of the dwarves nearby to the ring stopped their laughter, and turned to look at the rag-tag non-dwarven group that had just stumbled into the center of the tavern. Grog caught up to his friends and caught one of the dwarves staring up at him.

``What're \textit{you} lookin' at?" he sneered at the gawking dwarf.

For a very breif moment, the dwarf was sat silent. ``\textit{Well!}" he suddenly began, looking left and right to his fellows sitting beside him at the table before returning his gaze to the mountain of a being in the middle of the tavern. ``It's not very often we catch someone with \textit{that} kind of a mug on ya'! Le'me buy ya' a drink, \textit{come}, sit down!" The dwarf waived his hand in a motion for Grog to join them while some of the others began hitting the table with their hands--- another motion meaning for the goliath to join them in the festivities immediately.

``Oh!" Scanlan straightened with surprise.

``Aww..." Keyleth said as she grinned ear to ear, delighted by the kindess of the stranger towards her friend.

``My kind of people," Grog said to his friends that he had entered the tavern with before adding ``see you later!" and jovially turned to sit with his new dwarven buddies for a free drink. The rest of the party, between smiles and small-talk to each other, decided to take the table next to Grog and his new dwarven pals. Before they could, Vax'ildan realised that both of the tables adjacent to Grog were entirely taken by other dwarves, so he reached into a pocket and pulled out a sack of gold. 

Vex'ahlia, realising his sudden exposure of the large quantity of money without a clue as to what he was about to do with it, in a shocked voice that she strained to not let turn into a yell said to him; ``A \textit{sack} of gold, \textit{are you crazy?!}"

Continuing without any regard for his sister's surprise and worry, Vax'ildan slammed the sack of gold onto one of the dwarf-seated tables adjacent to the table Grog had sat and begun to drink at, bringing the shocked and now disgruntled dwarves' conversation to a sudden halt.

``\textit{Gentlemens} and \textit{ladies}," he started in the clearest announcing voice he could muster. Some of the other nearby tables began to quiet down. He scanned the bar to his left and right as he continued; ``\textit{Ladies} and \textit{gentlemen}, we are traveling from \textit{far} away. We just arrived from Emon. We are \textit{fascinated} to see your underground city, and to celebrate the occasion---" he lifted a single finger and began to draw it from one side of the room to the other, meaning so as to point to each patron currently in the bar, ``---I would like to buy \textit{every dwarf in here a round}." One by one, the dwarven eyes in the room had began to turn towards the table at which he stood. Faces sitting at tables just out front of the tavern peeked through open window to understand what had caused the silence. Vax'ildan, unfazed and unimpeded by the sudden attention he was gaining, in a single motion, brought his extended finger into a fist, and as he moved his fist back toward himself uttered a single word, more command than question; 

\begin{center}
    ``\textit{Bartender!}"
\end{center}

The faint music in the background of the tavern stopped mid-beat. All dwarven eyes in the bar turned to the table near the center of the room.

Scanlan stood grinning from ear to ear, his eyes darting back and forth throughout the room from face to face.

Percival's eyebrows were lifted in both surprise and worry, his mouth left agape and his glasses slightly askew.

Grog had put down the drink the dwarves had given him and turned to look at his black-clothed friend who had just offered everyone a drink with the same emotions as Percival painted across his face.

Pike, still caught up in her own thoughts had silently kept up with the group, and paid no mind to the dramatic goings on around her as she leaned her back on a nearby support column decoratively hewn from the same stone as the rest of the city.

Vex'ahlia, realising what her brother had done as well as why, had changed tune, and was now smiling at him while leaning on Trinket and stroking his fur.

Tiberius stood still with his hands behind his back, the vertical slits of his pupils more visible as he stared wide-eyed at the scene Vax'ildan had just created in the large, and rather occupied tavern.

Keyleth slowly turned her head from left to right, silently looking around the tavern with a huge open-mouth smile at the event unfolding before her.

All those same dwarven eyes then turned away from Vax'ildan to a single dwarven woman who stood at the back of one of the bars with a towel over one arm. She had begun to look around confused at the sudden quieting of the tavern, and had been directing most of her bewildered gaze at Vax'ildan. As the eyes turned one by one to her in silence, and for a moment she stared back. Suddenly, she threw up her free arm and shouted out in a heavily accented voice, ``\textit{Well}, it's about time somebody around here had some generosity!" She nodded towards Vax'ildan as she rushed through saying, ``Certainly, pay up front---" before ecstatically announcing to the rest of the bar's patrons, ``---\textit{Drinks} a-round on \textit{this} half-elven gentleman!"

Smiling faces throughout the bar turned back to the half-elf as he threw his right fist straight up into the air and single-handedly restarted the festivities of the tavern; ``Let it rain!"

Instantly, cheers boomed throughout the tavern, with Grog among those celebrating. He leaned over to Vax'ildan, yelling to be heard over the now much louder sounds of the room, ``\textit{I} would like a cask of ale." he said smugly, wearing a child-like smile as he asked his friend for the extra-large serving of ale, ready for the drinking to begin. 

Vax'ildan clasped an open palm on the back of Grog's large outstretched arm, and pointed to the happily busied bartender with his free hand. ``I'll need your largest bowl of ale for this one here!" he yelled to her over the renewed chorus of laughter and cheers.

``Cask!" Grog corrected him, and pantomimed holding a large barrel in front of his chest for the bartender to see. ``Cask of ale. Cask"

The dwarf smiled chuckled at Grog's request before yelling back from the bar, ``No worries, Adra's got your back," adding before she wandered off to the back room, ``be right back!" We she returned she began to pour stein after stein after stein of ale to the waiting patrons. 

``Yeah." Grog nodded approvingly when finally it came to be his turn. ``Keep going. Looks good." he finished once she had poured his stein full to the brim with ale. Over time, as Adra ran around the tavern, it became apparent that she was the head of the tavern with quite the number of barkeeps--- all of whom seemed to be male, with each and every one looking like they've been worked rather ragged.

Some time past, and eventually Scanlan raised himself off his chair and headed to the bar. ``Excuse me, miss. You." He raised a finger as he called out to Adra.

She whipped around to his attention from behind the bar; ``Adra, Yeay."

`I'm sorry, what?"

``Adra." She repeated, sounding slightly winded.

``Adra!" He gave a quick nod; Scanlan threw open his palms adding; ``You run a \textit{fantastic} establishment." 

``That's \textit{right} I do!" she said proudly, allowing a bit of her exhaust to show through as she moved an empty stein from her hand to in front of her to lean forward and rest her weight on it with both hands like a makeshift cane on the bar top. 

``Thank you for welcoming us," Scanlan continued, ``and allowing us to buy this round."

``Of course. Patrons that come and drop coin like \textit{that} are \textit{always} welcome." 

``Well, thank you for your hospitality." He thought as he continued; ``ah--- M-might we inquire about staying here for the night? Do you have an inn with the establishment?"

She reached below the counter top of the bar and pulled out a large tome which began to thumb through. One by one, she quickly skimmed over each page in a dog-eared section of the tome until her eyebrows lifted and her hand stopped moving over the page. ``You know, actually we have openings right now on the second floor."

``Ahm--- several rooms or just one?" he turned his head slightly to the side and steepled the tips of his fingers together while waiting for her response.

``Do you need them side by side?" Adra looked up from the tome and held her hands vertically and shoulder-width apart, as if they were two walls as she moved them up and down slightly.

``Eh, that would be nice." Scanlan smiled as he said appreciatively.

Focusing herself back into her tome, she began to mutter to herself as she re-arranged her temporary tenants under the vibrant noise of the tavern. ``... huh, we could pull 'im outta there, and push 'im into room seven..."

``\textit{Something} with a---" he sheepishly drew his open hands together to a small parallel distance during his interjection into her concentration, ``\textit{little} bed for me, please." 

First looking up, then to her side, she called out for one of her barmaiders. ``\textit{Giles!}" A moment later, one of the dwarven barmaiders came to the bar.

``\textit{Aye$\sim$?}" Giles said, exhaustion the only emotion in his voice.

``Get Stepheson out of 'is room, move him to the third floor. We have to open a block for our \textit{new guests}." she gestured to Scanlan and his companions seated well behind him in the middle of the tavern.

``Ugh, \textit{fine}, fine." The older dwarf left, begrudgingly stumbling up the stairs. Scanlan, while this happened, brought the rest of his companions over to the bar to finish up the preparations for the reservations with Adra.

``Ah--- alright." She clapped her hands together, back in focus. ``So, I can get a room for each of you." In a single, experienced sweep of a pointed finger to the group on the opposite side of the bar top from her, counted the group as she continued to speak. ``We're lookin' at eight rooms separately, that will run you, per evening, about ..." Looking up, she silently mouthed the mental math before looking forward and finishing; ``twenty-five gold pieces. Does that sound about right?"

Vex'ahlia turn away and suppressed a heave at what she understood from the dwarf.

Grog tilted his head down and looked concernedly at Adra from under his raised eyebrows. ``Total?" Grog finally asked the question on the groups' minds.

She nodded as she waived her circle in a hand and reiterated, ``Twenty-five \textbf{total} pieces." 

They collectively breathed a sigh of relief, but at least outwardly, Tiberius, Vax'ildan, and Percival seemed unfazed.

``Oh," Scanlan clapped his hands together in understanding. "Okay."

``You want to share a room?" Vex'ahlia asked Keyleth, gesturing back and forth between them with an upward pointed finger.

``Oh! Yeah, sure, we can bunk up." Keyleth happily agreed, glad to help cut the price of a their stay.

``Grog, you and me." Scanlan grabbed the goliath's attention as Percival and Tiberius spoke between themselves as did the other members of the group. ``I can sleep on your feet."

``Yeah, Scanlan and I'll ... we're ..." Grog trailed off into a wide-eyed quiet as he lost his train of thought, distracted by his friends all speaking at once. Pike, though paying attention, still remained deep within her own thoughts, and made no objection to having her own room. Just as quickly, they quieted down and finished counting that they'd be fine with just five rooms, so Vex'ahlia turned back to Adra and, in full confidence, proposed her own price for the now lessened number of rooms to rent.

``Probably like 15 gold then, for just that amount." She washing her hand back and forth while she spoke as if clearing some pipe smoke from before her.

Adra visibly deflated a bit, but couldn't bring herself to disagree with the newcomers that had just ensured her a well-payed night of work in her own tavern. ``All right, fair enough. Five rooms it is." Her shoulders dropped a bit as she continued. ``Fifteen gold per room." 

``We're penny pinchers." Scanlan added nervously.

Adra continued dutifully; ``How long do you expect to stay?"

``Oh!" Tiberius perked up and leaned forward toward Adra to make himself more heard. ``Ahrm, well, at least a \textit{few} days."

``I'd say at least a week." Scanlan corrected, and Tiberius nodded in agreement.

``---With an indefinite hold, we are--- we have ..." Percival searched for the right explanation. ``... we have business in the city." No one in the group came forward to add any further information.

``Right!" Adra, still too happy to have open-pocketed patrons such as these in her tavern, couldn't care why they were staying in town, but wanted desperately to keep them in \textit{her} tavern during their stay. ``Well how about we pay the week in advance and I'll give you a discount?"

``What's the discount?" Vex'ahlia didn't miss a beat in following up the offer with her question as Tiberius said, now mostly to himself, ``Oh! I \textit{love} discounts..."

``Wait, wait, wait, wait, wait, wait," Keyleth spoke up as Adra re-calculated for a discounted week's worth of five room's rent. ``I thought we were going to be heading .. south, like ..." she left the sentence unfinished, visibly confused, though none of her friends came to answer her question immediately. Adra, however, had finished her mental mathematics.

``Let's say 100 gold for the week, all five rooms." Adra had placed down her bargain, and hoped the group would bite.

A moment's silence between the head barmaid and the group of travelers passed, after which Vax'ildan spoke up. ``We're pretty flushed," he said to his companions. ``I think we can handle it."

``Yes, that works." Vex'ahlia agreed, but obvious hesitation was leveled in her voice.

``This doesn't terrify me." Percival added nonchalantly.

``Sounds good!" Scanlan concurred.

Finally overcome by her peers' pressuring her as the impromptu deal-maker, Vex'ahlia gave in. ``Gah! Fine!" She pulled a small pouch of coin from a pocket and after quickly counting the money in front of Adra, slid the small mound of gold over the bar top.


\newpage

%-----------------------------------------------
%----------------------END----------------------
%-----------------------------------------------